\chapter{简单句的扩展}

\section{主语的扩展}

英语中，句子的主语可以通过增添不定式、
分词、with结构、并列主语、同位语、
并列定语等方式进行扩展。

\begin{enumerate}
	\item 增添不定式 \\ His efforts \emph{to carry out} the task is admirable. \\ Her reluctance \emph{to do it} troubles us.
	\item 增添分词 \\ The letter \emph{written in eighteen century} is now very valuable. \\ The book \emph{being studied} is a classical novel.
	\item 增添with结构 \\ A woman \emph{with a baby in her arm} entered the room. \\ An old man \emph{with some teeth missing} was sitting under the tree.
	\item 增添并列主语 \\  \emph{Fame, money and position} are what he aspires. \\ \emph{Playing football and dancing} are his favorites.
	\item 增添同位语 \\ His aim, \emph{to realize his early dreams}, will be achieved. \\ His only hobby, \emph{going fishing}, has brought him a lot of benefits.
	\item 增添并列定语 \\ The ability \emph{to give correct judgment and to make decisions} is important  to a leader. \\ The girl \emph{sitting and reading} there is his daughter.
	\item 上述方式的综合使用。 \\ A great book, rich in ideas and beauty, a book that raises and tries to answer great fundamental questions, demands the most active reading of which you are capable.
\end{enumerate}

\section{谓语的扩展}

英语中，句子的谓语可以通过增添不定式、
并列成分、空间状语、方式状语、程度状语、
评注性状语、分词、独立结构以及介词短语等方式进行扩展。

\begin{enumerate}
	\item 增添不定式 \\ She appeared \emph{to have suffered} a lot.\\ He will never get \emph{to understand} it.
	\item 增添并列成分 \\ She neither \emph{hates} nor \emph{loves} him. \\ He \emph{has been, is} and \emph{will be} remembered for his noble character and great deeds.
	\item 增添空间状语 \\ An old pine tree stood \emph{in front of his house}. \\ Mongolia lies \emph{on the north of China}.
	\item 增添方式状语 \\ He faces the accident \emph{calmly}. \\ He cooked \emph{in the English style}.
	\item 增添分词（组） \\ He was gazing into the distance, \emph{lost in thought}. \\ \emph{Given more time}, we could do it well.
	\item 增添独立结构 \\ She held her daughter, \emph{tears streaming down her face}. \\ \emph{So many people being absent}, they cancelled the meeting.
	\item 增添介词短语 \\ \emph{With your help}, I am sure to succeed. \\ \emph{In the event of snow}, the match will be cancelled. \\
	      注：下列介词或介词短语可用于谓语的扩展，如：with a view to, for \ldots good, for the benefit of, with an eye to, for the good of, for the sake of, for fear of,  for the purpose of, with the object (intent, aim) of, in spite of, despite, regardless off, disregarding, for all that, for all the world, at all events, at any rate, in any event, at all cost
	\item 增添程度状语 \\ She \emph{obviously} enjoys the music. \\ I \emph{fully} agree with you. \\
	      注：nearly, virtually, barely, in the least, scarcely, practically, kind of, sufficiently, more or less, slightly, in part, a bit, merely, in some respects, to some extent, somewhat, a little bit, considerably, fairly, violently, enormously, definitely, utterly, in all respects等程度状语均可用于谓语的扩展。
	\item 增添评注状语 \\ \emph{Quite honestly}, he is not qualified for the job. \\ \emph{To my amazement}, he won the gold medal. \\
	      注：surprisingly, presumably, understandably, surely, naturally, interestingly,  personally, generally, hopefully, apparently, amazingly, fundamentally, theoretically, frankly, essentially, as a matter of fact, in all frankness, to one’s regret, without doubt, to tell the truth, to be fair, to be precise, to make matter worse, to be exact等评注状语均可用于谓语的扩展。\\
	      \emph{Obviously},the pictures are comparing two different attitudes towards study. （2020,英语一）\\
	      With people’s increasing greed for money, the reason why some feshmen ignore the annual fishing ban in dog  days and take the risk of violating the law to catch fish in the sea is that they want to acquire high economic profit by catching more fish, which \emph{unfortunately} and \emph{seriously} destroys the ecological balance of oceans. （2000,英语一）\\
	      The line chart above \emph{accurately} demonstates the statistics about museums and their visitors in China. （2017,英语二）
\end{enumerate}

\section{表语的扩展}

\begin{enumerate}
	\item be+形容词+不定式（主语是不定式的逻辑主语，为动词的执行者）。\\
	      She is willing \emph{to lend} me the money. \\
	      He is stupid \emph{to say} that. \\
	      注：slow, eager, willing, prepared, frightened, depressed, amazed, powerless, unqualified, unable, contented, impatient, liable, reluctant,\\ thoughtful, silly, unwise, inconsiderate, anxious, decent, brave, crazy, cruel, hesitant, naughty, furious等后均可接不定式用于表语的扩张。
	\item be+形容词+不定式（主语与不定式是动宾关系，为动作的承受者）。\\
	      Her words are hard \emph{to understand}. \\
	      She is pleasant \emph{to talk with}. \\
	      注：nice, useful, ready, dangerous, fit, nasty, pleasant, convenient, sufficient, cheap, awkward, easy, expensive, horrible, simple, hard, awful, amusing, impossible, strange, funny, interesting, extraordinary等都属于这类形容词，接不定式用于表语的扩张。
	\item be+形容词+to（to为介词）
	      He is blind \emph{to} his own mistake.\\
	      She is indifferent \emph{to} such trifles.\\
	      注：similar, equal, dear, close, respectful, sensitive, true, superior, inferior, loyal, sincere, kind, due, accustomed, subject等皆为这类形容词，均可用于表语的扩张。
	\item be+形容词+at\\
	      I am disgusted \emph{at} his words.\\
	      She is alarmed \emph{at} the sound.\\
	      注：clever, pleased, no good, good, surprised, brilliant, better, astonished, puzzled, angry, bad, delighted等皆为这类形容词，均可用于表语的扩张。
	\item be+形容词+with\\
	      He is bored \emph{with} the man.\\
	      He is strict \emph{with} children.\\
	      注：familiar, uneasy, sick, concerned, busy, content, friendly, furious, filled, satisfied, occupied, comfortable, disappointed等皆为这类形容词，均可用于表语的扩张。
	\item be+形容词+of\\
	      I am convinced \emph{of} his honesty.\\
	      He is scared \emph{of} the snake.\\
	      注：glad, full, fond, tired, sure, ashamed, certain, aware, conscious, convinced, guilty, proud, short, sick等皆为这类形容词，均可用于表语的扩张。
	\item be+形容词+about\\
	      He is mad \emph{about} money.\\
	      She is aggrieved \emph{about} the case.\\
	      注：happy, worried, reasonable, frightened, glad等皆为这类形容词，均可用于表语的扩张。
	\item be+形容词+from\\
	      He is free \emph{from} the duty.\\
	      It is far \emph{from} here.\\
	      注：different, absent, distant, remote等皆为这类形容词，均可用于表语的扩张。
	\item be+形容词+in\\
	      He is confident \emph{in} the work.\\
	      The boy is weak \emph{in} math.\\
	      注：absorbed, experienced, risk, poor, interested等皆为这类形容词，均可用于表语的扩张。
	\item be+形容词+on\\
	      She is intent \emph{on} the job.\\
	      He is reliant \emph{on} his father.\\
	      注：severe, keen, bent, based, dependent等皆为这类形容词，均可用于表语的扩张。
\end{enumerate}

\section{插入语}

在英语句子中，有些词、词组（短语）表示说话人的态度或看法，解释或说明，常用逗号同句中其他成分合开（也用破折号或括号），这就是插入语。插入语可居于句首、句中或句尾，视具体上下文而定，分为下面几类：

介词插入语：of course, by the way, in fact, in short, in my opinion, in other words, in general, by my estimate, to one’s surprise, to one’s amazement, to one regret\ldots

形容词插入语：worse still, strange enough, least possible, curious \\ enough, most important\ldots

副词 插入语：clearly, apparently, frankly, basically, personally, probably, possibly, luckily, hopefully, definitely, indeed, maybe, perhaps\ldots

分词插入语：generally speaking, judging from, frankly speaking, strictly speaking\ldots

不定式插入语：to start with, so to speak, to be sure, to sum up, to be precise, to tell the truth

短句插入语：that is, as it is/was 事实上， as I see it, as I know it, as far as I am concerned, as it were好像， if I may say so, I suppose, it seems

注意，插入语的使用是实现句子结构多样性的方法之一。例如：

\emph{Unlike western media}, newspapers in China usually report the positive development, \emph{rather than the problems and emergencies}, of the society.

Spending too much time planning for the future, \emph{as is argued by many people}, is a total waste of time. 
